### 2019-10-25 thesis/txt/0-introduction.tex
loads of corrections in ch2, literature, dev mails geschrieben und ausgewertet

CI builds produce long and verbose build logs~\cite{beller2017oops}, stating the progress and results of the various steps within the build.
The structure of these logs changes greatly from project to project~\cite{staahl2014modeling} as it highly depends on the tools and environment used.
Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform\mention{ citation needed }.
Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project\mention{ citation needed vassallo beller}.
However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.

@@

Currently there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
Developers and researches have little support while choosing which technique to use for a retrieval task.
The goal for this thesis is to investigate different information retrieval techniques (IR techniques) and describe under which circumstances we recommend each of the techniques.

We aim to define a model to characterize different IR techniques as well as the information retrievable from CI build logs.
For our first research question we analyze which criteria influence the suitability of an IR technique.
We support our assumption by implementing and evaluating three techniques:
\begin{itemize}
  \item regular expression program synthesis from examples using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as TS) and
  \item simple keyword search (referred to as SKWS)
\end{itemize}
Our second research question asks in which cases PBE, TS and SKWS are suited to retrieve information from continuous integration build logs. RQ2 is refined into sub-questions along the criteria resulting from RQ1 and compares their instantiations for the three techniques: how many examples a technique needs to perform best, the accuracy of the retrieved output and how diverse the configuring examples can be structurally.
\begin{simplebox}{Research Questions}
\begin{itemize}
  \item[\textbf{RQ1:}] Which criteria influence the suitability of an information retrieval technique for CI build logs?
  \item[\textbf{RQ2:}] When are PBE, TS and SKWS suited to retrieve information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}
\end{simplebox}
To evaluate PBE, TS and SKWS we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories. Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.

@@

\paragraph{Our work contributes:}
\begin{itemize}
  \item A model of the retrievable information in CI build logs
  \item A model to characterize information retrieval techniques from CI build logs
  \item A model to characterize use case scenarios for information retrieval from CI build logs
  \item A tool unifying several information retrieval techniques namely:
        \begin{itemize}
          \item regular expression program synthesis from examples using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (TS), and
          \item a simple keyword search approach (SKWS)
        \end{itemize}
  \item The \emph{LogCollector}, a tool to gather build logs from Travis CI
  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the retrievals according to their structural position within the build log
        \end{itemize}
  \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
  \item A extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
\end{itemize}

This thesis first presents an overview over the related research, spanning from CI research, build log analysis and augmentation, and common \todo{production?} log processing over information retrieval techniques to program synthesis by examples.
Next, chapter \ref{sec:models} present our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs. It also introduces the three techniques, we focus on during our research evaluation.
Chapter \ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}. There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity and keyword search.
Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
\end{document}

>>>>

CI builds produce long and verbose build logs~\cite{beller2017oops}, stating the progress and results of the various steps within the build.
The structure of these logs changes greatly from project to project~\cite{staahl2014modeling} as it highly depends on the tools and environment used.
Build logs are a valuable data source. First of all, for developers, who read them to analyze why their build failed or how different stages of the build process perform.
Second, they are valuable for researchers, who can harvest the information contained in the logs --- and their metadata --- to study the software engineering process of a project~\cite{rausch2017empirical,beller2017oops,seo2014programmers,vassallo2017a-tale}.
However, these two groups can only utilize the information within the build logs if they can adequately retrieve the information relevant to them.

@@

Currently there is only anecdotal evidence on the performance of these techniques and when a technique should be preferred.
Developers and researches have little support while choosing which technique to use for a retrieval task.
The goal of this thesis is to investigate different information retrieval techniques (IR techniques) and describe under which circumstances we recommend each of the techniques.

We aim to define a model to characterize different IR techniques, as well as the information retrievable from CI build logs.
For our first research question, we analyze which criteria influence the suitability of an IR technique.
We support our assumption by implementing and evaluating three techniques:
\begin{itemize}
  \item regular expression program synthesis from examples using the Microsoft PROSE library (referred to as PBE),
  \item a common text similarity approach (referred to as TS) and
  \item simple keyword search (referred to as SKWS)
\end{itemize}
Our second research question asks in which cases PBE, TS and SKWS are suited to retrieve information from continuous integration build logs. RQ2 is refined into sub-questions along the criteria resulting from RQ1 and compares their instantiations for the three techniques: how many examples a technique needs to perform best, the accuracy of the retrieved output and how structurally diverse the configuring examples can be.
\begin{simplebox}{Research Questions}
\begin{itemize}
  \item[\textbf{RQ1:}] Which criteria influence the suitability of an information retrieval technique for CI build logs?
  \item[\textbf{RQ2:}] When are PBE, TS, and SKWS suited to retrieve information from CI build logs?
  \item[\textbf{RQ2.1:}] How many examples do PBE, TS, and SKWS need to perform best?
  \item[\textbf{RQ2.2:}] How accurate are the retrievals of PBE, TS, and SKWS?
  \item[\textbf{RQ2.3:}] How structurally similar do the examples for PBE and TS need to be for the techniques to be applicable?
\end{itemize}
\end{simplebox}
To evaluate PBE, TS and SKWS we create the \emph{Failing Build Logs Data Set}, which encompasses about 800 log files from 80 repositories. Each log is labeled with the log part describing the reason a build failed, keywords to search for this log part and a categorization of the labeled log part according to its structural position within the log.

@@

\paragraph{Our work contributes:}
\begin{itemize}
  \item A model of the retrievable information in CI build logs
  \item A model to characterize information retrieval techniques from CI build logs
  \item A model to characterize use case scenarios for information retrieval from CI build logs
  \item A tool unifying several information retrieval techniques namely:
        \begin{itemize}
          \item regular expression program synthesis from examples using the Microsoft PROSE library (PBE),
          \item a common information retrieval approach using text similarity (TS), and
          \item a simple keyword search approach (SKWS)
        \end{itemize}
  \item The \emph{LogCollector}, a tool to gather build logs from Travis CI
  \item A validated data set of about 800 logs from failed Travis CI builds labeled with:
        \begin{itemize}
          \item the substring of the log describing the reason the build failed,
          \item keywords developers would use to search for these descriptions of the build failure reason, and
          \item a categorization of the retrievals according to their structural position within the build log
        \end{itemize}
  \item An evaluation of our model for the three implemented information retrieval techniques \todo{describe \emph{what} we look for with this evaluation}
  \item An extendable scheme supporting decision on (our three) information retrieval techniques relative to a given use case scenario
\end{itemize}

This thesis first presents an overview of the related research, spanning from CI research, build log analysis and augmentation, and common system log processing over information retrieval techniques to program synthesis by examples.
Next, chapter \ref{sec:models} presents our models for information retrieval techniques, use case scenarios for such techniques and retrievable information from CI build logs. It also introduces the three techniques, we focus on during our research evaluation.
Chapter \ref{sec:data-set} describes the creation of our \emph{Failing Build Logs Data Set} collected from failed Travis CI build logs and the labeling as well as the validation process.
Following, Chapter \ref{sec:implementation} our implementation of the three chosen information retrieval techniques and the usage of our unified information retrieval tool.
This tool is also used for the evaluation study of our models described in Chapter \ref{sec:study}. There we also describe the resulting instantiation of our recommendation model for regex program synthesis, text similarity, and keyword search.
Lastly, we conclude and give an overview of further research opportunities in Chapter \ref{sec:conclusion}.
\end{document}

### 2019-10-25 thesis/txt/2-models.tex
loads of corrections in ch2, literature, dev mails geschrieben und ausgewertet

\begin{itemize}
	\item \todo{look for more in modelling paper zampetti}
	\item Pulling the new, changed version of the source code onto the server.
	\item Running static analysis tools~\cite{zampetti2017open}.
	\item Building the software, i.e. compiling and packaging it~\cite{phillips2014understanding}.
	\item Running automated tests~\cite{beller2017oops}.
\end{itemize}

However these are only \emph{typical} stages and there is a high variability in the CI build processes of different software projects \mention{citation needed, zampetti2017open?}.
Some smaller projects might use CI to just make sure their code compiles as a minimal check before reviewing a pull request.
Other projects might have various stages of extensive automated testing.

Software tools involved in the build write out log messages to the console \mention{citation needed, paper about usages of console.log?}.
They communicate progress updates, error and warning messages to the user.
We refer to to the sum of this output as build log.
The structure of their output is chosen by every tool themselves.
Many have implicit or explicit structuring rules, some adhere to predefined standards \mention{phpunit, ruby, xuint output?}.
Figure \ref{fig:tool-log-contribution} shows how different tools contribute to the whole build log.

@@

\section{Retrievable Information in Build Logs}
\plan{fix naming, then review again}
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth, clip]{img/build-log-information.pdf}
	\caption{Information retrievable from build logs}
	\label{fig:build-log-information}
\end{figure}
Continuous integration build logs contain a huge amount of information about the various stages in the CI build they correspond to.
In this section we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
Figure \ref{fig:build-log-information} shows the model.

@@

During our initial exploration and log data collection for the \emph{Failing Build Log Data Set}, we collected a broad set of build logs from 29 languages and 87 repositories.
We inspected them to get an impression about the information one would want to retrieve from a build log.
Within the build logs from Travis CI we found various different information types possibly interesting to be retrieved:

@@

	\item \textbf{WarningMessage} In addition to errors, tools also print warning messages.
	      These could be collected, counted and presented to developers, encouraging them to resolve them in order to improve their software.
	      You can see examples of WarningMessage instantiations within build logs in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.

@@

\subsection{Method}
In/Output examples (I/O examples) are the main driver of Programming by Example.
When extracting information from build logs the \emph{input} is always a whole build log, i.e. the whole text of the build log file without any preprocessing.
In the implementation we did have to apply a few text replacements as described in \ref{sec:impl-preprocessing}.
The \emph{output} is always a substring of the log file text, representing the substring that should be extracted by the synthesized program when given the corresponding input file.
One or multiple I/O examples are needed as configuration for PBE, they are used to define substring of a log should be extracted.Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm. Both are described in \todo{ref rw sections}.
%For execution PBE takes a build file as input and returns a substring of the build file content.

@@

When studying the applicability of PBE from the \emph{usability} perspective you run into questions like
\begin{itemize}
	\item Are users faster when using PBE compared to manual regex construction?
	\item Are users more comfortable using PBE over manual regex construction?
	\item Are users confident in the resulting regular expression program from PBE?
	\item Are the resulting extractions more or less accurate when using PBE over manual regex construction?
\end{itemize}
Some of these were already evaluated in existing works about PBE and user interaction~\cite{mayer2015user} \mention{other works?}.
Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on syntesizing programs from examples in an unknow interface.
Mayer et al.~\cite{mayer2015user} presented two system-user interaction models to improve the confidence of users into the programs synthesized from their examples.
We feel such questions of usability can be answered separately from the application domain of build logs.

For our work we chose to look at the applicability of PBE from the \emph{technical} perspective.
We investigate whether current program synthesis techniques are able to learn programs for information retrieval tasks in the domain of CI build logs.
Furthermore we gather insights in how PBE has to be applied to yield useable results and perform best.
Our implementation of PBE \todo{which we name technique name x}, is mainly based on the Flash Extract DSL~\cite{flahsextractpaper} of the PROSE library by Microsoft\mention{cite prose website}.
Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.

@@

\subsection{Overview}
Text Similarity approaches are more and more used to filter unstructured textual software artifacts. \mention{cite papers that do exactily this. also lda possbible here}
One common and simple technique the Vector Space Model \mention{citation needed, for VSM and that it is common maybe?}.
We investigate when it is a suitable technique to retrieve information from build logs.
In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (TS), the concrete implementation is described in \ref{sec:impl-ts}.
Figure \ref{fig:text-similarity-explanation} shows the instantiation of the BLIRT model for TS.

@@

First, the search query is processed.
The output strings of the example set configuring the technique are split into single lines.
For each line we apply preprocessing: Splitting it into tokens, in our case words.
%Commonly text similarity techniques employ further normalization like removing special characters and stop words.
%We chose to keep the build log lines as complete as possible, as we often saw special characters and words identifying an interesting area.
Then we build a document-term-frequency matrix over the lines of the output strings and prune very often or very rarely appearing words.
Next, the algorithm applies term-frequency inverse document frequency, a best practice for natural language queries~\cite{lee1997document}.
To retrieve the desired information from a build log, we parse the whole text and process it in the same way.
The algorithm calculates the cosine simlarity~\mention{citation?} to compare each line of the build log with each line of the search query.
After summing up the similarities of each build log line to all the query lines, we sort the build log lines in decreasing similarity.
The average number of lines in the I/O example output strings determines how many of the most similar lines are returned as the output of the retrieval run.

%Information retrieval techniques are more and more prevalently used to extract textual information from unstructured textual sources~\mention{stuff annibale is referencing?}. We describe CI build logs as semi-structured,

\begin{figure}[hp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/skws-technique.pdf}
		\caption{Retrieving Information Using Simple Keyword Search}
		\label{fig:keword-search-explanation}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/diff-technique.pdf}
		\caption{Retrieving Information Using Amar et al.'s Line Diff Approach}
		\label{fig:diff-technique-model}
	\end{minipage}
\end{figure}

@@

\section{Further Techniques}
\plan{decide: what to mention here, max 1 page text}
\todo{maybe: instantiate model, or at least partly talk about it}
\todo{diffing, manual regex?, other summarization?, BART? <- we could reference that from related work then}

>>>>

\begin{itemize}
	\item Pulling the new, changed version of the source code onto the server.
	\item Running static analysis tools~\cite{zampetti2017open}.
	\item Building the software, i.e. compiling and packaging it~\cite{phillips2014understanding}.
	\item Running automated tests~\cite{beller2017oops}.
	\item Deployment of the build artifact~\cite{schermann2016empirical}.
\end{itemize}

However these are only \emph{typical} stages and there is a high variability in the CI build processes of different software projects~\cite{staahl2014modeling}.
Some smaller projects might use CI to just make sure their code compiles as a minimal check before reviewing a pull request.
Other projects might have various stages of extensive automated testing.

Software tools involved in the build write out log messages to the console.
They communicate progress updates, error and warning messages to the user~\cite{yuan2012characterizing}.
We refer to to the sum of this output as build log.
The structure of their output is chosen by every tool themselves.
Many have implicit or explicit structuring rules, some adhere to predefined standards like RSpec or PHPUnit~\cite{phpunit2019logging,rspec2019format}.
Figure \ref{fig:tool-log-contribution} shows how different tools contribute to the whole build log.

@@

\section{Retrievable Information in Build Logs}
\plan{fix naming, then review again}
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth, clip]{img/build-log-information.pdf}
	\caption{Information retrievable from build logs}
	\label{fig:build-log-information}
\end{figure}
Continuous integration build logs contain a huge amount of information about the stages in the CI build they correspond to.
In this section we present a model, which more precisely describes our notion of a information retrievable from a CI build log.
Figure \ref{fig:build-log-information} shows the model.

@@

During our initial exploration and log data collection for the \emph{Failing Build Log Data Set}, we collected a broad set of build logs from 29 languages and 87 repositories from Travis CI~\cite{travisci2019webpage}.
We inspected them to get an impression about the information one would want to retrieve from a build log.
Within the build logs from Travis CI we found different information types possibly interesting to be retrieved:

@@

	\item \textbf{WarningMessage} In addition to errors, tools also print warning messages.
	      These could be collected, counted and presented to developers, encouraging them to resolve them to improve their software.
	      You can see examples of WarningMessage instantiations within build logs in Figure \ref{fig:log-4} and Figure \ref{fig:log-5}.

@@

\subsection{Method}
In/Output examples (I/O examples) are the main driver of Programming by Example.
When extracting information from build logs the \emph{input} is always a whole build log, i.e. the whole text of the build log file without any preprocessing.
In the implementation we did have to apply a few text replacements as described in \ref{sec:impl-preprocessing}.
The \emph{output} is always a substring of the log file text, representing the substring that should be extracted by the synthesized program when given the corresponding input file.
One or multiple I/O examples are needed as configuration for PBE, they are used to define substring of a log should be extracted.Our approach is based on the Flash Extract DSL, which in turn is based on the FlashMeta algorithm. Both are described in Section \ref{sec:rw-prose}.
%For execution PBE takes a build file as input and returns a substring of the build file content.

@@

When studying the applicability of PBE from the \emph{usability} perspective you run into questions like
\begin{itemize}
	\item Are users faster when using PBE compared to manual regex construction?
	\item Are users more comfortable using PBE over manual regex construction?
	\item Are users confident in the resulting regular expression program from PBE?
	\item Are the resulting extractions more or less accurate when using PBE over manual regex construction?
\end{itemize}
Some of these were already evaluated in existing works about PBE and user interaction~\cite{mayer2015user,lau2009why-programming-by-demonstration,miller2001outlier}.
Adequately answering those questions is however highly dependent on the user interface and the corresponding interaction model used during a study.
Developers who are accustomed to crunching on regular expressions in their favorite IDE or Editor might have an adversely negative view on synthesizing programs from examples in an unknow interface.
Mayer et al.~\cite{mayer2015user} presented two system-user interaction models to improve the confidence of users into the programs synthesized from their examples.
We feel such questions of usability can be answered separately from the application domain of build logs.

For our work we chose to look at the applicability of PBE from the \emph{technical} perspective.
We investigate whether current program synthesis techniques are able to learn programs for information retrieval tasks in the domain of CI build logs.
Furthermore we gather insights in how PBE has to be applied to yield useable results and perform best.
Our implementation of PBE, is mainly based on the Flash Extract DSL~\cite{le2014flashextract:} of the PROSE library by Microsoft~\cite{prose2019webpage}.
Due to that our technique of text extraction through regular expression programs synthesized is highly influenced by the capabilities of Flash Extract.

@@

\subsection{Overview}
Text Similarity approaches are more and more used to filter unstructured textual software artifacts~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
One common and simple technique the Vector Space Model~\cite{schutze2008introduction}.
We investigate when it is a suitable technique to retrieve information from build logs.
In the following we will explain the concept of how we apply text similarity to information retrieval from CI build logs (TS), the concrete implementation is described in \ref{sec:impl-ts}.
Figure \ref{fig:text-similarity-explanation} shows the instantiation of the BLIRT model for TS.

@@

First, the search query is processed.
The output strings of the example set configuring the technique are split into single lines.
For each line we apply preprocessing: Splitting it into tokens, in our case words.
%Commonly text similarity techniques employ further normalization like removing special characters and stop words.
%We chose to keep the build log lines as complete as possible, as we often saw special characters and words identifying an interesting area.
Then we build a document-term-frequency matrix over the lines of the output strings and prune very often or very rarely appearing words.
Next, the algorithm applies term-frequency inverse document frequency, a best practice for natural language queries~\cite{lee1997document}.
To retrieve the desired information from a build log, we parse the whole text and process it in the same way.
The algorithm calculates the cosine simlarity~\cite{korenius2007principal} to compare each line of the build log with each line of the search query.
After summing up the similarities of each build log line to all the query lines, we sort the build log lines in decreasing similarity.
The average number of lines in the I/O example output strings determines how many of the most similar lines are returned as the output of the retrieval run.

%Information retrieval techniques are more and more prevalently used to extract textual information from unstructured textual sources~\mention{stuff annibale is referencing?}.

\begin{figure}[hp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/skws-technique.pdf}
		\caption{Retrieving Information Using Simple Keyword Search}
		\label{fig:keyword-search-explanation}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/diff-technique.pdf}
		\caption{Retrieving Information Using Amar et al.'s Line Diff Approach}
		\label{fig:diff-technique-model}
	\end{minipage}
\end{figure}

@@

\section{Further Techniques}
\plan{decide: what to mention here, max 1 page text}

### 2019-10-25 thesis/txt/3-data-set.tex
loads of corrections in ch2, literature, dev mails geschrieben und ausgewertet

\label{sec:data-set}
\section{Motivation}
originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how strutured or unstructured they are.
Then labeling of one build log information, namely the reason the build failed, as well as keywords and stuructural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results

@@

\subsection{Sampling Repositories}
Our first task was to determine a set of repositories to query logs from. Our \texttt{GHTorrentParser} can query the GHTorrent dataset for the most popular languages on github and the most popular repositories for a given language. \emph{Popularity} in this case is defined as the number of watches. Our \texttt{TravisRequester} can then check for a given repository whether it uses Travis CI.

\subsection{Sampling Builds}
The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API, to obtain the newest builds for a given repository. As most builds on Travis CI are successful \mention{citation needed} we use a stratified sampling approach: \texttt{TravisRequester} saves the found builds in logs in buckets according to their state. We encountered the following states during our data collection passes:
\begin{itemize}
	\item \todo{fill /5 mins/}
\end{itemize}
\texttt{TravisRequester} saves up to a configured number of builds per state and searches through a configured number of maximum checked builds.

@@

\section{Collection Process}
For our inital data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
our impression?
\todo{image!}

@@

\subsection{Sending Mails to Developers}
\subsubsection{Introduction}
For the \emph{Failing Build Log Data Set} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with differen build logs and systems.
We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.

The person who probably knows best why a build failed is the one committing the changes which triggered the build.
If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
In this section we describe how we validate the extractions of the build failure reason the \emph{Failing Build Log Data Set} describes.
\subsubsection{Method}
Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information. 
\subsubsection{Results}
\subsubsection{Discussion}
\subsubsection{Threats to Validity}

@@

>>>>

\label{sec:data-set}
\section{Motivation}
originally: log collection to get impression of build logs from various projects, what possibly extractable information they contain and how structured or unstructured they are.
Then labeling of one build log information, namely the reason the build failed, as well as keywords and structural category to use in our evaluation and support our impressions about suitability of the techniques with quantitative results

@@

\subsection{Sampling Repositories}
Our first task was to determine a set of repositories to query logs from.
Our \texttt{GHTorrentParser} can query the GHTorrent~\cite{gousios2013ghtorrent} data set for the most popular languages on github and the most popular repositories for a given language.
\emph{Popularity} in this case is defined as the number of watches.
Our \texttt{TravisRequester} can then check for a given repository whether it uses Travis CI.

\subsection{Sampling Builds}
The \texttt{LogCollector} uses the \texttt{TravisRequester}, our tool querying the Travis API~\cite{travisci2019apidoc}, to obtain the newest builds for a given repository.
As most builds on Travis CI are successful \mention{citation needed} we use a stratified sampling approach: \texttt{TravisRequester} saves the found builds in logs in buckets according to their state.
We encountered the following states during our data collection passes:
\begin{itemize}
	\item \todo{fill /5 mins/}
\end{itemize}
\texttt{TravisRequester} saves up to a configured number of builds per state and searches through a configured number of maximum checked builds.

@@

\section{Collection Process}
For our initial data collection to get an impression of build logs from various projects and languages we used the \texttt{LogCollector} to gather from the 30 most popular languages, up to 3 repositories using Travis CI each and 3 logs per state for each of those repositories.
For the \emph{Failing Build Log Data Set} we again collected from the same selection of repositories though saved only 10 logs of the state \emph{failed} for each repository.
our impression?
\todo{image!}

@@

@@

\subsection{Sending Mails to Developers}
\subsubsection{Introduction}
For the \emph{Failing Build Log Data Set} we analyzed around 800 build logs from different repositories and tried to extract the part of the log which describes why the respective build failed.
As we are not involved in the development of any of the open source projects within our data set we could only rely on our previous experience with different build logs and systems.
We only looked into the logs and did not check the related configurations, so it is well possible that we extracted parts that do describe errors but the respective step failing is ignored by the configuration and the build failed for another reason.

The person who probably knows best why a build failed is the one committing the changes which triggered the build.
If the build was e.g.\ part of a pull request then developer likely looked at it and tried to fix it so the pull request could be accepted.
In this section we describe how we validate the extractions of the build failure reason the \emph{Failing Build Log Data Set} describes.
\subsubsection{Method}
Using the Travis API, for every build log in the data set we looked up the corresponding build and the committer information.
We grouped all commits triggered by one developer and sent out an email to each of them, asking whether the log part selected during our labeling was indeed describing the reason the build failed.Figure \ref{fig:dev-mail} shows one of the mails sent out.
The email included links to the corresponding commits, build overview and log file.
We asked the receivers to fill out a short survey in case our extraction was not correct.
Look at Figure \ref{fig:dev-survey} to get an impression of the survey.
In the survey we presented the selected log part and asked the developer to paste in the log part actually describing the failure reason or describe why we were wrong in their own words.
As some of the extractions we labeled are many lines long, we trimmed all down to 10 lines in order to keep the mail readable.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth, clip]{img/dev-mail.png}
	\caption{An example of the mails we sent out to developers for validation of our labeled log part}
	\label{fig:dev-mail}
\end{figure}
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth, clip]{img/dev-survey.png}
	\caption{Survey for the validation with developers}
	\label{fig:dev-survey}
\end{figure}

\begin{figure}[h]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/dev-mails/answers-received.pdf}
		\caption{Proportions of Mails and Logs answered, undelivered and unanswered}
		\label{fig:mails-answers-received}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/dev-mails/extraction-correct.pdf}
		\caption{Responses to our developer survey}
		\label{fig:mails-extraction-correct}
	\end{minipage}
\end{figure}

\subsubsection{Results}
In total we sent out mails to 246 developers, asking about 3.2 build logs on average.
32 of these mails could not be delivered, e.g. because they were addressed at noreply mail addresses.
These 32 mails related to 68 of the build logs.
We received answers from 61 developers, responding about 144 build logs.
The proportions of mails and logs answered about, not delivered and unanswered is shown in Figure \ref{fig:mails-answers-received}.

Of the 144 answers, 132 said our extraction was correct.
26 answered either "close, but not quite correct" or "no, the build failed for another reason".
We manually inspected these negative answers and found that extractions were correct after all.
This yields 12 log extractions in our example set that were not correct, shown in Figure \ref{fig:mails-extraction-correct}.

\subsubsection{Discussion}
This study highly strengthens the trust in the validity of the extracted build failure reasons in the \emph{Failing Build Log Data Set}.
The study received answers about 18\% of the logs labelled in our build log, of which, after manual correction, 91\% said our labelled extractions were accurate.

Most of the initial ``incorrect'' answers we adjusted in them manual inspection, stated that the proposed extraction did not show the whole reason the build failed.
This is because we had to trim long labeled extractions to keep the emails readable.

One of our extractions only showed a warning and the developer propose to also include the line above, stating that warnings are treated as errors in the build.
In others that were identified as ``incorrect'' we labelled the error message of an error that later ignored and did not lead to the build failing.

\subsubsection{Threats to Validity}
